Leadership across cultures and contexts: an exploratory analysis

### 2020-05-18 leadership_across_cultures_contexts.Rmd
Spell check

To determine which leader qualitiy and function dimensions were associated with evidence for high status leaders, we fit an elasticnet logistic model of *High status* as a function of all quality and function dimensions, (with the lasso penalty, $\alpha = 1$). The non-zero coefficients indicated that *Punishment*, the only identified function, was a negative predictor, whereas
<!-- all other functions, including *Organize cooperation*, *Ritual functions*, and *Provide counsel/direction* were non-predictors, and  -->
*Wealthy*, *Strategic nepotism*, *Age*, *Experienced/accomplished*, and several other qualities, were positive predictors. See Figure \@ref(fig:highstatusplot)B.

@@

Our revised model proposes that leaders deploy cognitive, social, material, and somatic capital to provide benefits and impose costs on followers. If their abilities to provide benefits or impose costs are similar to other groups members, as in "chiefs-for-a-day", they acquire little status, but if their abilities are exceptional relative to other group members, they gain status via biological market mechanisms [@hammerstein_biological_2016; @garfield_evolutionary_2019; @hagen_leadership_2019; @pietraszewski_evolution_2019]. There was particulary strong evidence for cognitive and social capital, with cognitive capital associated with both providing benefits and imposing costs, particularly among shaman leaders (Figure \@ref(fig:fivefold)).

@@

Also, all texts records were in English. Some of the eHRAF docuements have been translated to English from the original language of publication. We did not investigate variation in original source language (i.e., translated to English vs. written in English). Lastly, The eHRAF provides an evalutation of each document on a non-mutually exclusive five-point scale ranging from poor, acceptable, good, or excellent sources of primary or secondary data; 98% of documents in our sample score 4 or higher, as excellent sources of primary or secondary data.

>>>>

To determine which leader quality and function dimensions were associated with evidence for high status leaders, we fit an elasticnet logistic model of *High status* as a function of all quality and function dimensions, (with the lasso penalty, $\alpha = 1$). The non-zero coefficients indicated that *Punishment*, the only identified function, was a negative predictor, whereas
<!-- all other functions, including *Organize cooperation*, *Ritual functions*, and *Provide counsel/direction* were non-predictors, and  -->
*Wealthy*, *Strategic nepotism*, *Age*, *Experienced/accomplished*, and several other qualities, were positive predictors. See Figure \@ref(fig:highstatusplot)B.

@@

Our revised model proposes that leaders deploy cognitive, social, material, and somatic capital to provide benefits and impose costs on followers. If their abilities to provide benefits or impose costs are similar to other groups members, as in "chiefs-for-a-day", they acquire little status, but if their abilities are exceptional relative to other group members, they gain status via biological market mechanisms [@hammerstein_biological_2016; @garfield_evolutionary_2019; @hagen_leadership_2019; @pietraszewski_evolution_2019]. There was particularly strong evidence for cognitive and social capital, with cognitive capital associated with both providing benefits and imposing costs, particularly among shaman leaders (Figure \@ref(fig:fivefold)).

@@

Also, all texts records were in English. Some of the eHRAF documents have been translated to English from the original language of publication. We did not investigate variation in original source language (i.e., translated to English vs. written in English). Lastly, The eHRAF provides an evaluation of each document on a non-mutually exclusive five-point scale ranging from poor, acceptable, good, or excellent sources of primary or secondary data; 98% of documents in our sample score 4 or higher, as excellent sources of primary or secondary data.
